BivData Setup

### 2020-01-27 src/BivData_Setup.Rmd
re-ran the setup with corrected FULL data csvs

update IFD functions, to add IFD2,3

@@

@@

#adding more feature calculations (IFD, ect)
Curated_BivData <- add_IFD(Curated_BivData)
Curated_BivData$IFD1_PER = Curated_BivData$IFD1_ABS / Curated_BivData$chromosomeLength

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_1.22.20.RData")
#save.image("data/BivData_4_PCA.RData")

>>>>

update IFD functions, to add IFD2,3 -- report the summaries

@@

```{r input.check,echo=FALSE}

#check for mistakes that might have been made when inputing / curation process

#hand foci > 4

#foci pos > SC lengths

#negative PER.foci.pos

#it hink most (ALL) of these came from bug in my function (ugh)

#Curated_BivData <- add_IFD(Curated_BivData)
#negative.IFD <- Curated_BivData[which(Curated_BivData$IFD1_ABS < 0),]
#caught 2
#15mar16_16jan16_G_f1_sp1_4_rev
#27mar16_6mar16_G_m3_sp1_12_rev

#neg Nrm F1
#negative.IFD2 <- Curated_BivData[which(Curated_BivData$PER_Foci_1 < 0),]
#0 really?
```

@@

#adding more feature calculations (IFD, ect)
Curated_BivData <- add_IFD(Curated_BivData)#fixed a bug
Curated_BivData$IFD1_PER = Curated_BivData$IFD1_ABS / Curated_BivData$chromosomeLength

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_1.27.20.RData")
#save.image("data/BivData_4_PCA.RData")
